---
title: "Group11 Presentation"
output: ioslides_presentation
---

```{r setup, include=FALSE}

library(kableExtra)
library(jtools)
library(huxtable)
library(tinytex)
```

## Introduction 

- USDA Data on pesticides used on strawberries for California, Florida, Oregon, and Washington, from 2016 - 2019
- Toxicity records on different toxins 
- Our question: If the toxicity level of toxins would leave to lower usage of toxins in terms of lbs?

```{r data, echo = F, warning = F, include = F}
## source in data 
source("wrangling_data.R", echo = T, prompt.echo = "", spaced = F)
```

## Florida has the highest usage of toxins in lbs measurement, and the toxicity level is low

- Lowest lbs usage of pesticides in Florida in 2018
- Highest lbs usage of pesticides in Florida in 2016 

```{r tabl1, echo = FALSE}
tb1 <- agg_df2 %>% 
  filter(measure == "APPLICATIONS, MEASURED IN LB")%>%
  filter(toxicity_level!="")%>%
  group_by(State, Year,toxicity_level)%>%
  summarise(value = mean(Value))%>%
  kbl(caption = "Table 1.Absolute usaged of chemicals at different toxicity level by year") %>%
  kable_classic_2(full_width = F)
tb1
```

## California has more pesticides used are measured in lbs on strawberries 

- While Florida has much lower number for pesticides used are measured in lbs 
- Most pesticides used in California are either no toxins or low toxins

```{r table2, echo=FALSE}
tb2 <- agg_df2 %>%
  filter(measure == "APPLICATIONS, MEASURED IN LB")%>%
  filter(toxicity_level!="")%>%
  group_by(State, toxicity_level)%>%
  summarise(n = n())%>%
  spread(toxicity_level,n)%>%
  kbl(caption = "Table 2.Total count of chemicals all used in absoluate LB by state and toxicity levels") %>%
  kable_classic_2(full_width = F)
tb2
```

## Florida has the highest average lbs pesticides used 

```{r map, echo=FALSE}
p <- ggplot(data = toxicity_val,
           aes(x = long, y = lat,
               group = group, fill = value))+
      geom_polygon(color = "gray90", size = 0.1) +
      coord_map(projection = "albers", lat0 = 39, lat1 = 45) +
      ggtitle("Map-average usaged of toxins")
p
```


## Modeling: is there a relationship on toxicity and usage of pesticides (measured in lbs)?

```{r model}
fit <- lm(Value ~ toxicity_humanbee_cat+toxicity_level_cat, data = agg_df2)
summ(fit)
```

## Conclusion 

- No clear relationship between toxicity/toxicity level and usaged of pesticides (measured in lbs)

- Future imrovement: 
1. More data; 
2. Include natural environment variables 
3. Using proportional usage of pesticides 